Artificial ecosystem selection on soil methane oxidation reveals simple/complex

### 2020-07-16 Manuscript/manuscript.Rmd
Remove old rank-based response to selection

```{r sel_model}
fluxes <- read_tsv('../Output/fluxes.tsv')
rank_fit <- lm(estimate_rank ~ treat * passage, data = fluxes)

sel_sum <- tidy(summary(rank_fit))
sel_aov <- tidy(anova(rank_fit))
```

Methane oxidation rates increased over the course of the experiment in the positive selection treatment and did not change in the neutral selection treatment (`r figures("selection", display="cite")`). This can be seen in the significant interaction between treatment and passage number for the rank of CH~4~ oxidation rate (F~`r sel_aov[3,2]`,`r sel_aov[4,2]`~ = `r myround(sel_aov[3,5], 2)`, p = `r myround(sel_aov[3,6], 3)`). While there was no difference in the overall mean of the two treatments (F~`r sel_aov[1,2]`,`r sel_aov[4,2]`~ = `r myround(sel_aov[1,5], 2)`, p = `r myround(sel_aov[1,6], 2)`), the mean rank CH~4~ oxidation rate increased by `r myround(sel_sum[4,2],1)`  per passage for the positive selection treatment (t = `r myround(sel_sum[4, 4], 2)`, p = `r myround(sel_sum[4, 5], 3)`), but the neutral treatment did not change ($\beta$ = `r myround(sel_sum[3,2],1)`, t = `r myround(sel_sum[3,4], 2)`, p = `r myround(sel_sum[3,5], 2)`).

```{r sel_fig, fig.width=5, fig.height=3, fig.cap=figures("selection")}
fluxes %>% 
  ggplot(mapping = aes(x = passage, y = estimate_rank, color = treat)) +
  geom_jitter(width = 0.2) +
  geom_smooth(method = 'lm', formula = y ~ x, se = FALSE) +
  labs(x = "Passage Number", y = "Rank Methane Oxidation Rate (-k)") +
  #scale_color_discrete(name = "Selection\nTreatment", labels = c('Neutral', 'Positive')) +
    scale_color_manual(name = "Selection\nTreatment", labels = c('Neutral', 'Positive'), values = c("gray60", "darkorange2")) +
  theme_bw()
```

## Deviance

```{r dev_model}
deviance_se <- 
  fluxes %>% 
  select(treat, passage, estimate) %>% 
  group_by(passage, treat) %>% 
  summarize(se = se(estimate)) %>% 
  pivot_wider(names_from = treat, values_from = se) %>% 
  mutate(deviance_se = p + n) %>% 
  pull(deviance_se)

>>>>

```{r dev_model}
fluxes <- read_tsv('../Output/fluxes.tsv')

deviance_se <- 
  fluxes %>% 
  select(treat, passage, estimate) %>% 
  group_by(passage, treat) %>% 
  summarize(se = se(estimate)) %>% 
  pivot_wider(names_from = treat, values_from = se) %>% 
  mutate(deviance_se = p + n) %>% 
  pull(deviance_se)
